A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/dtpddl.tex
New controller spec

\noindent To model the sensing capabilities of the agent, we have
operator-like descriptive elements, with preconditions in both action
and state symbols, and uniformly positive effects over perceptual
predicates -- I.e, the negation normal form of a sensing effect
formula cannot contain negation. Whereas the effects of an {\em
operator} schema are over state propositions, and describe how the
states change under application of actions, the effects of a {\em
sense} schema are perceptual, and describe the composition of an
observation following the execution of an action. Also, and without a
loss of generality, we find it convenient to separate the actional
precondition from the state precondition.

Making the above ideas concrete with an example, suppose a robot is
able to look for a visual-object, such as a box, at a given place. We
can model that deterministic action using the following operator
schema:

>>>>

\noindent To model the sensing capabilities of the agent, we have
operator-like descriptive elements, with preconditions in both action
and state symbols, and uniformly positive effects over perceptual
predicates -- I.e, the negation normal form of a sensing effect
formula cannot contain negation. Whereas the effects of an {\em
operator} schema are over state propositions, specifying how the
states change under application of actions, the effects of a {\em
sense} schema are perceptual, specifying the composition of an
observation following the execution of an action. Also, and without a
loss of generality, we find it convenient to separate the actional
precondition from the state precondition.

Making the above ideas concrete with an example, suppose a robot is
able to look for a visual-object, such as a $\pp{box}$, at a given place. We
can model that deterministic action using the following operator
schema:
